What's in a Name? Linear Temporal Logic Literally Represents Time Lines

### 2023-01-02 paper/main.tex
typo

We gather a test suite of 91 formulas used in real-world requirement specification. We take $6$ specifications from NASA's Automated Airspace Concept (AAC)\cite{GCMTR16}. We also collect formulas from the Acacia suite of examples \cite{RV10}. We reap $85$ formulas from the suit of $23$ examples, by generating seperate visualizations for each line of specification. % We choose to visualize each formula specifically, rather than complete specifications, as

We run \texttt{ltl2regex} on these $91$ examples, the tool completes execution (within timeout of $20$s) on $87$. Within the $87$, two examples have regular expressions of star height $8$ and are intractible to generate graph visualizations of. We are able to generate tractible visualization on the $85$, or over $93\%$ of benchmarks tested. The plots of visualization complexity on these formula are provided below in \cref{fig:real-world}.

@@

\appendix
\section{Concrete Syntax of \tool} \label{sec:concrete-syntax}
Recall from \ref{ltl-defn} that we define \ltl\ formula as
\begin{align*}
    \Phi ::= p \mid \neg \Phi \mid \Phi \land \Phi \mid \Phi \lor \Phi \mid \Phi \limplies \Phi \mid \always \Phi \mid \eventually \Phi \mid \nextt \Phi \mid \Phi \stronguntil \Phi \mid \Phi \weakrelease \Phi
\end{align*}
where $p \in \AP$. In our tool \tool, we use the following concrete syntax to represent \ltl\ formulae.
\[
    \begin{array}{c r l l l@{\qquad} l}
         &      & \textit{abstract syntax}              & \textit{concrete syntax}                       & \textit{description} \\
    \Phi & ::=  & p                                     & \texttt{p}                                     & \text{atomic proposition} \\
         & \mid & \neg \Phi                             & \texttt{!} \Phi                                & \text{negation} \\
         & \mid & \Phi \land \Phi                       & \Phi \texttt{ \& } \Phi                        & \text{conjunction} \\
         & \mid & \Phi \lor \Phi                        & \Phi \texttt{ | } \Phi                         & \text{disjunction} \\
         & \mid & \Phi \limplies \Phi                   & \Phi \texttt{ -> } \Phi                        & \text{implication} \\
         & \mid & \always \Phi                          & \texttt{G} \Phi                                & \text{globally} \\
         & \mid & \eventually \Phi                      & \texttt{F} \Phi                                & \text{finally} \\
         & \mid & \nextt \Phi                           & \texttt{X} \Phi                                & \text{next} \\
         & \mid & \Phi \stronguntil \Phi                & \Phi \texttt{ U } \Phi                         & \text{until} \\
         & \mid & \Phi \weakrelease \Phi                & \Phi \texttt{ R } \Phi                         & \text{release} \\
    \end{array}
\]

\bibliographystyle{elsarticle-num}
\bibliography{RelatedWork}

>>>>

We gather a test suite of 91 formulas used in real-world requirement specification. We take $6$ specifications from NASA's Automated Airspace Concept (AAC)\cite{GCMTR16}. We also collect formulas from the Acacia suite of examples \cite{RV10}. We reap $85$ formulas from the suite of $23$ examples, by generating separate visualizations for each line of specification. % We choose to visualize each formula specifically, rather than complete specifications, as

We run \texttt{ltl2regex} on these $91$ examples, the tool completes execution (within timeout of $20$s) on $87$. Within the $87$, two examples have regular expressions of star height $8$ and are intractable to generate graph visualizations of. We are able to generate tractable visualization on the $85$, or over $93\%$, of benchmarks tested. The plots of visualization complexity on these formula are provided below in \cref{fig:real-world}.

@@

\appendix
\section{Concrete Syntax of \tool} \label{sec:concrete-syntax}
Recall from \ref{ltl-defn} that we define \ltl\ formula as
\begin{align*}
    \Phi ::= p \mid \neg \Phi \mid \Phi \land \Phi \mid \Phi \lor \Phi \mid \Phi \limplies \Phi \mid \always \Phi \mid \eventually \Phi \mid \nextt \Phi \mid \Phi \stronguntil \Phi \mid \Phi \weakrelease \Phi
\end{align*}
where $p \in \AP$. In our tool \tool, we use the following concrete syntax to represent \ltl\ formulae.
\[
    \begin{array}{c r l l l@{\qquad} l}
         &      & \textit{abstract syntax}              & \textit{concrete syntax}                       & \textit{description} \\
    \Phi & ::=  & p                                     & \texttt{p}                                     & \text{atomic proposition} \\
         & \mid & \neg \Phi                             & \texttt{!} \Phi                                & \text{negation} \\
         & \mid & \Phi \land \Phi                       & \Phi \texttt{ \& } \Phi                        & \text{conjunction} \\
         & \mid & \Phi \lor \Phi                        & \Phi \texttt{ | } \Phi                         & \text{disjunction} \\
         & \mid & \Phi \limplies \Phi                   & \Phi \texttt{ -> } \Phi                        & \text{implication} \\
         & \mid & \always \Phi                          & \texttt{G} \Phi                                & \text{globally} \\
         & \mid & \eventually \Phi                      & \texttt{F} \Phi                                & \text{finally} \\
         & \mid & \nextt \Phi                           & \texttt{X} \Phi                                & \text{next} \\
         & \mid & \Phi \stronguntil \Phi                & \Phi \texttt{ U } \Phi                         & \text{until} \\
         & \mid & \Phi \weakrelease \Phi                & \Phi \texttt{ R } \Phi                         & \text{release} \\
    \end{array}
\]
%\nocite{*}
\bibliographystyle{elsarticle-num}
\bibliography{RelatedWork}
